European or American? A re-examination of the transatlantic influence over the IMF

### 2025-05-22 manuscript/manuscript.qmd
Add functional forms

>>>>

\begin{align*}
Y^*_{it} &= \alpha + \beta_1 \text{USA}_{it} + \beta_2 \text{EUP}_{it} + \gamma^\top \mathbf{P}_{it} + \delta^\top \mathbf{Z}_{it} + \lambda_t + \epsilon_{it} \\
Y_{it} &= \begin{cases}
          0~\text{if}~ Y_{it}^* \leq 0 \\
          Y_{it}^* ~\text{if}~ 0 < Y_{it}^* < c\\
          c ~\text{if}~ Y_{it}^* \geq c \\
          \end{cases}
\end{align*}

$$
\mathbf{P}_{it} = \left( \ln(\text{GDP}_{it}), \ln(\text{GDP}_{it})^2, \ln(\text{PCGDP}_{it}), \ln(\text{PCGDP}_{it})^2 \right)^\top
$$

$$
\Pr(Y_{it}=1)=\Phi(\alpha + \beta_1 \text{USA}_{it} + \beta_2 \text{EUP}_{it} + \gamma^\top \mathbf{P}_{it} + \delta^\top \mathbf{Z}_{it} + \lambda_t)
$$
